### 2024-02-14 paper_sisc_first_revision/localpsf.tex
addglr and psf  results from frog vs length_scale
discussion with noemi and tucker, include HODLR

x1 = (0.5, 0.5)
y = (y1, y2)
Phi((y1, y2), (x1, x2)) = Phi(y,x)

@@

>>>>

@@

Define HODLR. Define randomized HODLR algo. Ref to Tucker's paper and "Fast randomized eigensolver with structured LDL..."

Define randomized SVD, refer to Halko Martinsson Tropp.

Discuss why PSF does better with smaller $L$.

\begin{table}
	\begin{center}
		{\small
		\begingroup
		\setlength{\tabcolsep}{8pt}
		\renewcommand{\arraystretch}{1.0}
		\begin{tabular}{c| c | c c c c c}
						& Error tol.    &	\#applies PSF   & \#applies HODLR 	& rank \\ 
			\hline 
						& 20\%    		& 11  				& 592				& 37  \\ 
			$L=1$ 		& 10\% 			& 15  				& 772				& 67  \\ 
						& 5\% 			& 23   				& 924				& 100 \\ 
			\hline
						& 20\%    		& 8  				& 852 				& 143 \\ 
			$L=1/2$ 	& 10\%    		& 10  				& 1144				& 256 \\ 
						& 5\% 	  		& 12   				& 1404				& 377 \\ 
			\hline
						& 20\%    	 	& 7					& 932				& 294  \\ 
			$L=1/3$ 	& 10\%    		& 8  				& 1264 				& 525  \\ 
						& 5\% 			& 8   				& 1520 				& 767  \\ 
		\end{tabular}
		\endgroup
	}
	\end{center}
	\caption{(Spatially variant blur) Comparison of cost to approximate the blur kernel from Equation \eqref{eq:frog_kernel} using the PSF method, the randomized HODLR (hierarchical off diagonal low rank) method, and GLR (global low rank) approximation using randomized SVD. The quantity $L$ scales the width of the impulse responses, hence it influences the rank of the operator. Large $L$ means low rank, and small $L$ means high rank. The second column (``Error tol'') is the relative error in the approximation of the kernel measured in the Frobenius norm, $||\Phi - \widetilde{\Phi}||_\text{Fro} / ||\Phi||_\text{Fro}$. The remaining three columns show the number of operator applies require to achieve the given error tolerance, using the PSF, HODLR, and GLR methods.}
	\label{tab:frog_psf_vs_hodlr_vs_glr}
\end{table}
